---
title: "Predictive Models for Fraud Detection"
date: "`r Sys.Date()`"
author: Emilio Brenes
output:
  rmdformats::readthedown:
    highlight: kate
---


```{r setup, echo=TRUE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=TRUE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

```{r}
wd <- getwd()
setwd(wd)

library(ggplot2)
library(ggpubr)
library(stats)
library(cluster)
library(mclust)
library(factoextra)
library(dendextend)
library(DT)
library(tidyverse)
library(dplyr)
library(purrr)
library(tidygraph)
library(ROCR)
library(e1071)
library(randomForest)
library(rpart)
library(caret)
library(reshape2)
library(plotly)
library(AppliedPredictiveModeling)
library(caTools)
library(imputeTS)
library(nnet)
library(recipes)
library(kernlab)
library(ranger)
library(gbm)
library(randomForest)
library(doParallel)
library(modelgrid)
library(klaR)
```

# Data Wrangling

```{r}
datos <- read_csv("../datos.fraude.train.csv")
datos <- datos[,-1]
attach(datos)
summary(datos)
```


```{r}
datos$Class <- if_else(datos$Class == 1, "Si", "No")
datos$Class <- as.factor(datos$Class)

any(!complete.cases(datos))
```

```{r}
ggplot(data = datos, aes(x = Class, y = stat(count),fill = Class))+
  geom_bar()+scale_fill_manual(values = c("gray50", "orangered2"))+
  labs(title = "Casos de Fraude")+
  theme_bw()+
  theme(legend.position = "bottom")
```

```{r}
df <- as.data.frame(table(datos$Class))
df$Porcentaje <- df$Freq/sum(df$Freq)
DT::datatable(df) %>% formatPercentage("Porcentaje", 3)
```


# Data Balancing and Partitioning

```{r}
# Downsample to balance data and aleviate computational capacity
x <- datos[,!(names(datos) %in% "Class")]
y <- datos$Class
datos <- downSample(x = x, y = y, list = FALSE)

df <- as.data.frame(table(datos$Class))
df$Porcentaje <- df$Freq/sum(df$Freq)
DT::datatable(df) %>% formatPercentage("Porcentaje", 3)
```

```{r}
train <- createDataPartition(datos$Class, times = 1, p = 0.8, list = FALSE)
data.train <- datos[train,]
data.test <- datos[-train,]
```


```{r}
pro.train <- as.data.frame(table(data.train$Class))
pro.test <- as.data.frame(table(data.test$Class))
colnames(pro.train) <- c("Class","F.Train")

pro.train$F.test <- pro.test$Freq

pro.train$P.train <- pro.train$F.Train/sum(pro.train$F.Train)
pro.test$P.test <- pro.train$F.test/sum(pro.train$F.test)

DT::datatable(pro.train)
```


# Data Preprocessing

```{r}
objeto.recipe <- recipe(formula = Class ~., data = datos)
objeto.recipe
```


```{r}
tmp <- datos %>% nearZeroVar(saveMetrics = TRUE)
DT::datatable(tmp)%>%formatPercentage("percentUnique",2)%>%formatRound("freqRatio",2)
```

```{r}
objeto.recipe <- objeto.recipe%>% step_nzv(all_predictors())

objeto.recipe <- objeto.recipe%>% step_center(all_numeric())
objeto.recipe <- objeto.recipe%>% step_scale(all_numeric())

trained.recipe <- prep(objeto.recipe, training = data.train)
trained.recipe
```

```{r}
data.train.prep <- bake(trained.recipe, new_data = data.train)
data.test.prep <- bake(trained.recipe, new_data = data.test)

glimpse(data.train.prep)
```


# Variable Selection

```{r}
workers<-makeCluster(4)
registerDoParallel(workers)

# Size of predictor sets
subsets <- c(4:30)

# Size of resamples for bootstraping
repeticiones <- 10

# Seeds
set.seed(123)
seeds <- vector(mode = "list", length = repeticiones + 1)
for (i in 1:repeticiones) {
  seeds[[i]] <- sample.int(1000, length(subsets))
} 
seeds[[repeticiones + 1]] <- sample.int(1000, 1)

# Training control
ctrl_rfe <- rfeControl(functions = rfFuncs, method = "boot", number = repeticiones,
                       returnResamp = "all", allowParallel = TRUE, verbose = FALSE,
                       seeds = seeds)

# Recursive elemination process of predictors
set.seed(342)
rf.rfe <- rfe(Class ~ ., data = data.train.prep,
              sizes = subsets,
              metric = "Accuracy",
              # Accuracy is the ratio of correct classifications
              rfeControl = ctrl_rfe,
              ntree = 250)

rf.rfe
```


After 8 variables, the mariginal increment in accuracy is minimal and the Kappa starts to diminish. Therefore, this will be the size of the predictor set.


```{r}
rf.rfe$results %>%
  group_by(Variables)%>%
  summarise(
    mean.acc = mean(Accuracy),
    mean.kappa = mean(Kappa)
  )%>%
  arrange(desc(mean.kappa))
```


```{r}
ggplot(data = rf.rfe$results, aes(x = Variables, y = Accuracy)) +
  geom_line() +
  scale_x_continuous(breaks  = unique(rf.rfe$results$Variables)) +
  geom_point() +
  geom_errorbar(aes(ymin = Accuracy - AccuracySD, ymax = Accuracy + AccuracySD),
                width = 0.2) +
  geom_point(data = rf.rfe$results %>% slice(which.max(Accuracy)),
             color = "red") +
  theme_bw()
```


```{r}
top8var <- rf.rfe$variables %>%
  filter(Variables == 8)%>%
  group_by(var)%>%
  summarise(
    mean = mean(Overall),
    sd = mean(Overall)
  )%>%
  arrange(desc(mean))

top.var <- top8var$var[1:8]
top.var
```

```{r}
rf.rfe$optVariables
```


# Model Training

```{r}
grid.modelos <- model_grid()
grid.modelos
```


```{r}
grid.modelos <- grid.modelos %>% 
  share_settings(
    y = data.train.prep$Class,
    x = data.train.prep %>% dplyr::select(top.var),
    metric = "Accuracy",
    trControl = trainControl(method = "repeatedcv",
                             number = 10,
                             repeats = 5,
                             returnResamp = "final",
                             verboseIter = FALSE,
                             allowParallel = TRUE
                             )
  )

grid.modelos <- grid.modelos %>%
  add_model(
    model_name = "RandomForest",
    method = "rf",
    num.trees  = 300,
    tuneGrid   = expand.grid(mtry = c(2,3,5))
  ) %>%
  add_model(
    model_name = "RegLogistica",
    method = "glm",
    family = binomial(link = "logit")
  ) %>%
  add_model(
    model_name = "SVM",
    method = "svmRadial",
    tuneGrid   = expand.grid(sigma = c(0.001, 0.01, 0.1, 0.5, 1),
                              C = c(1 , 20, 50, 100)
                             )
  )

```


```{r}
workers <- makeCluster(4)
registerDoParallel(workers)

grid.modelos <- train(grid.modelos, train_all = FALSE, resample_seed = 123)
grid.modelos$model_fits
```


```{r}
grid.modelos <- grid.modelos %>%
  add_model(
    model_name = "NaiveBayes",
    method = "nb"
  )%>%
  add_model(
    model_name = "KNN",
    method = "knn",
    tuneGrid = expand.grid(
      k = c(1, 2, 5, 10, 15, 20)
    )
  )%>% 
  add_model(
    model_name = "NeuralNets",
    method = "nnet",
    rang = c(-0.7, 0.7),
    trace = FALSE,
    tuneGrid = expand.grid(
      size = c(10, 20, 50),
      decay = c(0.0001, 0.1, 0.5)
    )
  )%>%
  add_model(
    model_name = "LDA",
    method = "lda"
  )

workers <- makeCluster(4)
registerDoParallel(workers)

grid.modelos <- train(grid.modelos, train_all = FALSE, resample_seed = 123)
grid.modelos$model_fits
```

# Model Error Evaluation

```{r}
metricas.cv <- as.data.frame(caret::resamples(x = grid.modelos$model_fits))%>%
  gather(key = "modelo", value = "valor",-Resample)

DT::datatable(metricas.cv %>% group_by(modelo) %>%
                summarise(Media_Precision = round(mean(valor),3) ) %>%
                arrange(desc(Media_Precision))
              )
```

```{r}
metricas.cv %>%
  group_by(modelo) %>% 
  summarise(media = mean(valor)) %>%
  ggplot(aes(x = reorder(modelo, media), y = media, label = round(media, 3))) +
    geom_segment(aes(x = reorder(modelo, media), y = 0,
                     xend = modelo, yend = media),
                     color = "grey50") +
    geom_point(size = 7, color = "firebrick") +
    geom_text(color = "white", size = 2.5) +
    scale_y_continuous(limits = c(0, 1)) +
    # Accuracy basal
    geom_hline(yintercept = 0.55, linetype = "dashed") +
    annotate(geom = "text", y = 0.72, x = 8.5, label = "Accuracy basal") +
    labs(title = "Validación: Accuracy medio repeated-CV",
         subtitle = "Modelos ordenados por media",
         x = "modelo") +
    coord_flip() +
    theme_bw()
```

```{r}
predicciones <- extractPrediction(models = grid.modelos$model_fits,
                          testX = data.test.prep %>% dplyr::select(top.var),
                          testY = data.test.prep$Class
                          )
DT::datatable(predicciones)
```


```{r}
metricas.predicciones <- predicciones %>%
                mutate(acierto = if_else(obs == pred,TRUE,FALSE))%>%
                group_by(model,dataType)%>%
                summarise(
                  accuracy = mean(acierto)
                )%>%
                arrange(desc(accuracy))
DT::datatable(metricas.predicciones)
```

```{r}
ggplot(data = metricas.predicciones,
       aes(x = reorder(model, accuracy), y = accuracy,
           color = dataType, label = round(accuracy, 2))) +
  geom_point(size = 8) +
  scale_color_manual(values = c("orangered2", "gray50")) +
  geom_text(color = "white", size = 3) +
  scale_y_continuous(limits = c(0, 1)) +
  # Accuracy basal
  geom_hline(yintercept = 0.55, linetype = "dashed") +
  annotate(geom = "text", y = 0.56, x = 8.5, label = "Accuracy basal") +
  coord_flip() +
  labs(title = "Accuracy de entrenamiento y test", 
       x = "modelo") +
  theme_bw() + 
  theme(legend.position = "bottom")
```

Although SVM and LogisticRegressoin produced the same accuracy on the test dataset, I opted for LR as the winner because it had less variation with the results of the training set. 

# Winner Model

```{r}
data.bake <- bake(trained.recipe, new_data = datos)

glm.modelo <- model_grid()
glm.modelo <- glm.modelo %>%
  share_settings(
    x = data.bake %>% dplyr::select(top.var),
    y = data.bake$Class,
    metric = "Accuracy",
    trControl = trainControl(
      method = "repeatedcv",
      number = 10,
      repeats = 5,
      returnResamp = "final",
      verboseIter = FALSE,
      allowParallel = TRUE
    )
  )
glm.modelo <- glm.modelo %>%
  add_model(
    model_name = "RegLogistica",
    method = "glm",
    family = binomial(link = "logit")
  )

workers <- makeCluster(4)
registerDoParallel(workers)

glm.modelo <- train(glm.modelo, train_all = FALSE, resample_seed = 123)
glm.modelo$model_fits
```


```{r}
testdata <- read_csv("../datos.fraude.test.csv")
id <- testdata$X1
testdata <- testdata[,-1]
testdata <- bake(trained.recipe, testdata)

predicciones.glm <- extractPrediction(
                    models = glm.modelo$model_fits,
                    unkX = testdata
                    )
predicciones.glm
```


```{r}
predicciones.fraude <- as.data.frame(cbind(id, predicciones.glm$pred))
colnames(predicciones.fraude) <- c("Id","Prediccion")
predicciones.fraude[,2] <- if_else(predicciones.fraude[,2] == "1","No","Si")

# write.csv(predicciones.fraude,
#           "C:\\Users\\pcEmilio\\Desktop\\Lead\\2020 Q1\\Mineria Avanzada\\Examen Final\\Fraud\\Predictions.csv", row.names = FALSE)
```

```{r}
saveRDS(glm.modelo$model_fits, "./winnerModel.rds")

# load the model
clasificadorGanador <- readRDS("./winnerModel.rds")
print(clasificadorGanador)
```













